Face Attractiveness and the Sense of Reality

### 2022-08-30 analysis.Rmd
minor

df <- read.csv("data/data.csv")
# |>
#   mutate(
#     Date = lubridate::dmy(Date),
#     Participant = fct_reorder(Participant, Date),
#     Screen_Refresh = as.character(Screen_Refresh),
#     Illusion_Side = as.factor(Illusion_Side),
#     # Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Null", "Congruent"),
#     Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
#     Block = as.factor(Block),
#     Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
#   )
```

@@

```{r message=FALSE, warning=FALSE}
df |>
  # mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
  #   summarize(Real = mean(Real)) |>
  #   ungroup() |>
  #   arrange(Real) |>
  #   pull(Participant))) |>
  mutate(Participant = fct_relevel(Participant, dfsub$Participant)) |> 
  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  scale_y_discrete(expand = c(1, 1)) +
  scale_x_continuous(
    limits = c(0, 1),
    expand = c(0, 0),
    breaks = c(0, 0.5, 1),
    label = c("Fake", "0", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    # axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

### Colinearity

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Real ~ poly(Attractive, 2) + poly(Trustworthy, 2) +
                            (1|Participant) + (1|Stimulus), data = df, family=glmmTMB::beta_family())
model <- mgcv::gamm(Real ~ s(Attractive) + Trustworthy, random = list(Participant=~1, Stimulus=~1), data = df, family=mgcv::betar())

@@

df |> 
  ggplot(aes(x = Attractive, y = Real)) +
  ggside::geom_xsidedensity(fill = "grey", color="white") +
  ggside::geom_ysidedensity(fill = "grey", color="white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_point2(alpha=0.25, size=4, color="white") +
  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = pred, aes(y = Predicted)) +
  scale_fill_viridis_c(guide="none") +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_continuous(expand=c(0, 0))

pred <- estimate_relation(model, at = c("Trustworthy"), length=20)

@@

>>>>

df <- read.csv("data/data.csv") |>
  mutate(
    Date = lubridate::dmy(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh)
#     Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
  )

# Create individual scores for Simulation Moniroting
df <- df |> 
  mutate(Belief = ifelse(SimulationMonitoring >= 0, "Real", "Fake")) |> 
  group_by(Participant, Belief) |> 
  summarise(Confidence = mean(abs(SimulationMonitoring))) |> 
  pivot_wider(names_from = "Belief", values_from = "Confidence") |> 
  transmute(Participant, ConfidenceReality=Real, ConfidenceSimulation=Fake) |> 
  merge(df, by="Participant")
```

@@

#### Real / Fake

```{r message=FALSE, warning=FALSE}
df |>
  # mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
  #   summarize(Real = mean(Real)) |>
  #   ungroup() |>
  #   arrange(Real) |>
  #   pull(Participant))) |>
  mutate(Participant = fct_relevel(Participant, dfsub$Participant)) |> 
  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  scale_y_discrete(expand = c(1, 1)) +
  scale_x_continuous(
    limits = c(0, 1),
    expand = c(0, 0),
    breaks = c(0, 0.5, 1),
    label = c("Fake", "", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    # axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

#### Colinearity

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Real ~ poly(Attractive, 2) +
                            (1|Participant) + (1|Stimulus), data = df, family=glmmTMB::beta_family())
model <- mgcv::gamm(Real ~ s(Attractive) + Trustworthy, random = list(Participant=~1, Stimulus=~1), data = df, family=mgcv::betar())

@@

df |> 
  ggplot(aes(x = Attractive, y = Real)) +
  ggside::geom_xsidedensity(fill = "grey", color="white") +
  ggside::geom_ysidedensity(fill = "grey", color="white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_point2(alpha=0.25, size=4, color="white") +
  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = pred, aes(y = Predicted)) +
  scale_fill_viridis_c(guide="none") +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_continuous(expand=c(0, 0))
```

### Reality and Trustworthiness

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Real ~ poly(Trustworthy, 2) +
                            (1|Participant) + (1|Stimulus), data = df, family=glmmTMB::beta_family())

```{r message=FALSE, warning=FALSE}
pred <- estimate_relation(model, at = c("Trustworthy"), length=20)

@@

### Reality and Familiarity

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Real ~ poly(Familiar, 2) +
                            (1|Participant) + (1|Stimulus), data = df, family=glmmTMB::beta_family())
model <- mgcv::gamm(Real ~ s(Attractive) + Trustworthy, random = list(Participant=~1, Stimulus=~1), data = df, family=mgcv::betar())

```{r message=FALSE, warning=FALSE}
pred <- estimate_relation(model, at = c("Familiar"), length=20)

df |> 
  ggplot(aes(x = Familiar, y = Real)) +
  ggside::geom_xsidedensity(fill = "grey", color="white") +
  ggside::geom_ysidedensity(fill = "grey", color="white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_point2(alpha=0.25, size=4, color="white") +
  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = pred, aes(y = Predicted)) +
  scale_fill_viridis_c(guide="none") +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_continuous(expand=c(0, 0))
```
